%auto-ignore
%      this ensures the arxiv doesn't try to start TeXing here.
%!TEX root = super_lattice_models_draft.tex
%      prev line helps TeXShop do the right thing



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fermion condensation in $\halfesix$} \label{halfesix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


In this section we perform fermion condensation in the category $\halfesix$.
This provides an example of a super pivotal category with fusion multiplicity.
After condensation we will obtain a theory with one non-trivial q-type particle, 
which we will denote by $\rho$.
$\rho$ obeys the fusion rule
\begin{align}
\rho \tp \rho = \mathbb{C}^{1|1} \mathds{1} \oplus \mathbb{C}^{1|1} \rho,
\end{align}
which is similar to the Fibonacci fusion rule but with q-type objects.\footnote{A simpler generalization of the Fibonacci theory 
to the super pivotal case, with one non-trivial q-type particle and fusion space 
$V^{\tilde{\tau} \tilde{\tau}}_{\tilde {\tau}}\cong \mathbb{C}^{1|1}$, does not exist. 
Indeed, suppose $\text{End}(\tau) = \mathbb{C} \ell_1$ and $V^{\tau \tau \tau} \cong \mathbb{C}^{1|1}$.
$\gamma \in \text{End}(\tau)$ denote the odd endomorphism in $V^{\tau\tau\tau}$.
Then we can write down three anti-commuting operators $\gamma \tp \gamma \tp 1$, $\gamma \tp 1 \tp \gamma$ and $1\tp \gamma \tp \gamma$ 
which are each even and as such preserve the grading on $V^{\tau\tau\tau}$. 
However, the even and odd subspaces of $V^{\tau\tau\tau}$ are one dimensional, and so these operators cannot be represented.
Hence a theory with a single q-type particle with Fibonacci-like fusion rules must have nontrivial fusion multiplicity.
In the $\halfesix$ theory we have $V^{\tau\tau\tau} \cong \cc^{2|2}$, which is big enough to represent all three of the above operators.}
The nontrivial fusion spaces are $V^{\rho\rho}_\rho \cong \cc^{2|2}$ and $V^{\rho\unit}_\rho \cong \cc^{1|1}$, 
with the first telling us that the theory has nontrivial fusion multiplicity. 


This theory is richer than the examples we have considered previously, and serves as a good 
case study for the features that appear in phases described by more general super pivotal 
categories. 
These more general features include:
\begin{itemize}
\item There is a quasiparticle excitation which has a non-bounding spin structure but which is m-type 
(this also occurs in the $SO(3)_6/\psi$ theory discussed previously) and is oddly self dual.
\item The ground state degeneracy on the three spin tori with a bounding cycle (with spin 
structures $BB$, $BN$, and $NB$) is $\mathbb{C}^{3|0}$, and the ground state degeneracy on the 
non-bounding torus (with $NN$ spin structure) is $\mathbb{C}^{1|2}$.
In particular, the fermion parity of a ground state on the torus is not uniquely determined by 
the torus' spin structure (this also occurs in the $SO(3)_6/\psi$ theory discussed previously). 
\item As a fusion category, there is a fusion rule that takes two q-type particles to another q-type particle.\footnote{
Note that fusion products of this type cannot appear in the tube category of a fermionic theory since two idempotents 
in the tube category with non-bounding spin structure must fuse to an idempotent with bounding spin structure, which can never be q-type.
}
\end{itemize}

Performing the condensation requires one additional step that did not appear in the previous examples. 
This is because the category $\halfesix$ is not braided, and so doesn't have a fermion to condense.
However, as described in Section \ref{lift_and_condense}, 
it suffices to lift a particle in $\halfesix$ to a fermion in the Drinfeld center of $\halfesix$.

In what follows, we will first introduce the fusion theory of $\halfesix$ 
and its properties that are pertinent to the rest of the section.
We will then compute the half braid for the emergent fermion, and condense it in the same way we did in the previous examples.
Following this, we will compute the idempotents in the condensed theory, 
as well as the modular $S$ and $T$ matrices. 



%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fusion theory of $\halfesix$}
\label{halfesixFusionTheory}
%%%%%%%%%%%%%%%%%%%%%%%%

The $E_6$ fusion category is the fusion category whose principle graph is given by the $\text{E}_6$ Dynkin diagram, 
shown to the left in Figure \ref{EsixDynkin}.
The $E_6$ fusion category has two sub-categories: one subcategory has the fusion rules of the Ising theory, 
while the other is known as $\halfesix$ \cite{Hong2008} and has more complicated fusion rules. 
\begin{figure}
\begin{align}
\vcenter{
\xymatrix @!0 @M=4mm @R=28mm @C=40mm{
&\EsixDynkin  &   &\EsixCondensePsi&  \\
&\HalfEsixDynkin &   &\HalfEsixDynkinCondensed&  \\
 	}} \nonumber
\end{align}
\caption{
On the upper left we have the $E_6$ Dynkin diagram. 
The $E_6$ fusion theory has two closed fusion subcategories whose simple objects are $\left \{ \mathds{1},\; \sigma,\; y \right\}$ and $\left \{ \mathds{1}, x,y \right \}$. 
The first satisfies the Ising fusion rules while the second satisfies those of $\halfesix$ given in (\ref{halfEsixFusionRules}).
The figure on the upper right denotes the principal graph of the theory after condensing $y$ (after first lifting $y$ to the Drinfeld center).
On the bottom left we have drawn the $\halfesix$ principal graph.
The figure on the bottom right is the principal graph of $\halfesix/y$ studied in this section.
The fermionic quotient of the $\halfesix$ fusion subcategory reduces the particle content to $\{\unit,\rho\}$.  
}
\label{EsixDynkin}
\end{figure}


The fusion category $\halfesix$ has three particles, $\mathds{1}$, $x$, and $y$. 
The non-trivial fusion rules are
\begin{align}
y \tp y \cong \mathds{1} \quad \quad y \tp x \cong x \tp y \cong x \quad \quad x\tp x \cong \mathds{1}\oplus 2x \oplus y,
\label{halfEsixFusionRules}
\end{align}
and the quantum dimensions are given by
\begin{align}
d_{\mathds{1}} = 1 \quad \quad d_x = 1 + \sqrt{3} \quad \quad d_y = 1.
\end{align}
Note that one of the fusion spaces ($V_x^{xx}$) has dimension greater than 1.
Note also that $x$ 
is invariant under fusion with $y$, and that $y$ has quantum dimension $1$. 
If the theory were braided, and $y$ were fermionic, then condensing $y$ would lead to a super pivotal 
fusion theory with only two objects, $\mathds{1}$ and $\rho$, the image of $x$ under condensation of $y$. 
This theory however is not braided, and so we will have to do more work to condense $y$, 
as discussed in the next subsection 
(see also the discussion in Section \ref{lift_and_condense}).

\medskip

We now lay out some of the basic data of $\halfesix$ which will be useful to us in the following sections. 
Specifically we will give all information required to manipulate the $y$ line, 
which will be useful knowledge to have on hand when we condense $y$. 

From looking at (\ref{halfEsixFusionRules}) we notice that all particles are self dual, 
and therefore we must specify their Frobenius-Schur indicators. 
In this case both Frobenius-Schur indicators are equal to 1.
These can be found from the associators $\kappa_x = d_x \left[ F^{xxx}_x \right]_{\mathds{1}\mathds{1}}$, and similarly for $y$. 
We list all the $F$-symbols (as found in \cite{okazaki2013,Wakui2002}) in App.~\ref{E6Fsymbols}.
Using the $F$-symbols in App.~\ref{E6Fsymbols} we can check that, in this gauge, $y$ has nice pivotal properties:
\begin{align}
\begin{matrix}
&{\xxypivotadual  = \xxypivotbdual  =  \Vxxydual} \\
&\\
&{\xxypivota =  \xxypivotb = \Vxxy } \\
\end{matrix}
&\;\;
\begin{matrix}
&{\yxxpivotadual = \yxxpivotbdual = \Vyxxdual }\\
&\\
&{\yxxpivota = \yxxpivotb=  \Vyxx }\\
\end{matrix}
&\;\;
\begin{matrix}
&{\xyxpivotadual = \xyxpivotbdual = \Vxyxdual } \\
&\\
&{\xyxpivota =  \xyxpivotb =  \Vxyx}\\
\end{matrix}
\end{align}
The fact that these diagrams are trivially pivotal is a reflection of the gauge choice used for the splitting spaces.

Next, we look at what happens when we slide a $y$ line past a $V^{xx}_x$ fusion space.
Since $\text{dim} V^{xx}_x = 2$ the fusion space requires a multiplicity index labeling the independent vectors spanning this vector space. 
We denote them $v_1$ and $v_2$, and diagrammatically label them with an index at the fusion vertex:
\begin{align}
V^{xx}_x \cong \mathbb{C} \left[\;\; \Vxxxa \;\;  \right  ] \qquad \qquad a = 1, 2.
\end{align}
The next three relations show what happens when $y$ shifts past the fusion space $V^{xx}_x$:
\begin{align}
\Vxyxxa = \sigma^x_{ab} \; \Vxyxxb
\quad \quad 
\Vyxxxa = \sigma^z_{ab} \;\; \Vyxxxb
\quad \quad 
\Vxxyxa =  \sigma^y_{ab} \;\Vxxyxb,
\label{yslide}
\end{align}
where the $\sigma^w$, $w = x,y,z$ are the standard Pauli matrices.\footnote{
Explicitly $\sigma^x = \left( \begin{matrix} 0 &1\\ 1&0 \end{matrix} \right) \quad  \sigma^y = \left( \begin{matrix} 0 &-i\\ i&0 \end{matrix} \right)  \quad \sigma^z = \left( \begin{matrix} 1 &0\\ 0&-1 \end{matrix} \right)$}
When we condense $y$, these sliding moves will determine the action of $\End(\rho) \tp \End(\rho) \tp \End(\rho)$ on $V^{\rho \rho}_\rho$.

Lastly, we have
\begin{align}
&\Vxxxva \; = \; \left( W_{\mathds{1}} \right)_{ab} \Vxxxvb \quad \quad 
W_{\mathds{1}} = \frac{e^{-7 i \pi /12}}{\sqrt{2}}\left( \begin{matrix} 1 &-i \\ 1 & i \end{matrix} \right) \\
\nonumber \\
&  \Vxxxya \; = \;  \left( W_{y} \right )_{ab} \; \Vxxxyb  \quad \quad   W_y = \frac{e^{-7 i \pi /12}}{\sqrt{2}}\left( \begin{matrix} 1 &-i \\ -1 & -i \end{matrix} \right)
\end{align}
These will be of use to us when we specify the pivotal properties of $\halfesix$ 
after condensing $y$; see Section \ref{ESixPivotal} for more details.
The only data left to specify is the associators for the $V^{xxx}_x$ fusion space, 
which we list in Appendix~\ref{E6Fsymbols}.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fermion condensation in $\halfesix$}
\label{condensey}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this subsection we will describe the procedure for condensing the $y$ particle in $\halfesix$. 
As mentioned earlier, $\halfesix$ is not braided, and so when we say condense $y$, 
we actually mean that we lift $y$ to the Drinfeld center (where it is an emergent fermion), and condense the lift of $y$. 
Since the center of $\halfesix$ has been computed in several places \cite{Hong2008,Izumi2001, kawahigashi2001} we will not provide all details. 

The lift of $y$ to the Drinfeld center can be found by solving \eqref{halfbraid_resolution} 
subject to the constraints \eqref{identityBraid} and \eqref{junctionBraid}.
Using the fusion theory of $\halfesix$ defined above in Section~\ref{halfesixFusionTheory} one readily finds the unique solution,
\begin{align}
\halfbraid{\ebox}{y}{\unit +x+y}{} = \halfbraid{\eone}{y}{\mathds{1}}{} - \; i   \halfbraid{\ex}{y}{x}{x} -   \halfbraid{\ey}{y}{y}{\mathds{1}}.
\label{yhalfbraid}
\end{align}
The negative sign on the last term makes the statistics and twist
of (the lift of) $y$ fermionic. 

We are now in a position to condense $y$.
Since $x$ is invariant under fusion with $y$ after condensation it becomes a q-type simple object, which we will denote by $\rho$:
\begin{align}
x \xrightarrow{\;\; \text{condense $y$\;\;}} \rho \quad \quad \quad \text{End}(\rho) \cong \mathbb{C} \ell_1
\end{align}
$\rho$ is the only non-trivial simple object in the condensed theory. 
Furthermore, since $x$ has fusion multiplicity in the parent theory, $\rho$ has fusion multiplicity in the condensed theory.
This is captured by the fusion space
\begin{align}
V^{\rho \rho}_\rho \cong \mathbb{C}^{2|2}.
\end{align}
The nontrivial fusion rule of the condensed theory is
\begin{align}
\rho \tp \rho = \mathbb{C}^{1|1}\cdot \mathds{1} \oplus \mathbb{C}^{1|1} \cdot \rho.
\end{align}
The fusion rule coefficients $\Delta^{\rho\rho}_\rho = \Delta^{\rho\rho}_\unit \cong \cc^{1|1}$ 
appearing in the above formula are determined by the relation $V^{ab}_c \cong \Delta^{ab}_c \tp \End(c)$ and the 
knowledge of the fusion spaces $V^{\rho\rho}_\rho \cong \cc^{2|2}, V^{\rho \unit}_\rho \cong \cc^{1|1}$.\footnote{We could have 
also taken $\Delta^{\rho \rho}_\rho \cong \cc^{2|0}$ or $ \cc^{0|2}$.
}






%%%%%%%%%%%%%%%%%%%%
\subsubsection{Pivotal structure}
\label{ESixPivotal}
%%%%%%%%%%%%%%%%%%%%

Since $\text{End}(\rho) \cong \cliff_1$, $\End(\rho)$ possesses an odd endomorphism which we will denote as $f$. 
We will denote the even basis vectors of $V^{\rho \rho}_\rho$ as $v_1$ and $v_2$, so that the odd basis 
vectors are $f {v_1}$ and $f {v_{2}}$, where the $f v_i$ are obtained by acting with $f$ on the bottom leg of the fusion space.
Diagrammatically we can denote this vector space by
\begin{align}
V^{\rho \rho }_\rho \; \cong \; \mathbb{C} \left[ \VSeven , \quad \VSa \right] \quad \quad \quad a = 1, 2,
\end{align}
where $f$ is represented graphically by the blue dot. 
We can then use our knowledge of local relations in the parent $\halfesix$ theory and the lift of $y$ to 
derive the following relations in the condensed theory:
\begin{align} 
\VSa = \sigma^z_{ab} \VSb \qquad \VSa = \sigma^y_{ab} \VSc \qquad \VSd = -i \sigma^x_{ab} \VSc,
\label{esixdotslide}
\end{align}
where the $\sigma^{w}$ are the standard Pauli matrices (compare \eqref{yslide}). 
We can also obtain the following pivoting moves:
 \begin{align}
 \PivotEsixEven  = 
P_{ab}\Vrhorhorho \quad \quad P = \frac{e^{7 i \pi/12}}{\sqrt{2}}\left( \begin{matrix}
 1& 1\\ 
 i &- i
 \end{matrix} \right)  \\
 \PivotEsixOdd =
\overset{\bullet}{P}_{ab} \Vrhorhorhoodd \quad \quad \overset{\bullet}{P} =  \frac{e^{7 i \pi/12}}{\sqrt{2}}\left( \begin{matrix} 
 i& -i\\ 
 -1 & -1
 \end{matrix} \right) 
 \end{align}
 Note that we have $P^3=\unit,( \overset{\bullet}{P} )^3=-\unit$, which is consistent with the fact that $P$ acts on even vectors 
 while $\overset{\bullet}{P}$ acts on odd ones (so that $(\overset{\bullet}{P})^3$ rotates an odd vector by $2\pi$, which produces a minus sign). 
 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\subsection{The tube category and the torus}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Tube category morphism spaces}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}
\centering
\scalebox{0.86}{
\begin{tabular}{ r  c c c }
&$e$&$h$&$\stackrel{\bullet}{h}$\\
\cline{2-4} 
&      &     &  \\[-2ex]
$\mor^B(e \ra e) $ 
&$\AddDat{\eTube}{B}{} $
&$\AddDat{\hTube}{B}{} $&\\
\\
$\mor^N(e \ra e) $ 
&$\AddDat{\eTube}{N}{} $
&&$\AddDat{\hTube}{N}{\dotb} $\\
\end{tabular}
}
\caption{A complete basis of morphisms for $\text{mor}^B(e \ra e) \in \tube(\halfesix/y)$.
The labels above each tube are short-hand for that tube: $e$ -- empty tube; $h$ -- tube with horizontal $\rho$ line. 
The dot above $h$ denotes that the morphism is an odd morphism.}
\label{etoe}

\bigskip
\bigskip



\scalebox{0.86}{
\begin{tabular}{ r  c c c }
&$k$&$\stackrel{\bullet}{k}$\\
\cline{2-3} 
&      &     \\[-2ex]
$\mor^B(\rho \ra e) $ 
&$\AddDat{\AddDat{\TaddownTubeprime{1}}{B}{}}{}{} $
&$\AddDat{\AddDat{\TaddownTubeprime{1}}{B}{\dota}}{}{} $\\
\\
$\mor^N(\rho \ra e) $ 
&$\AddDat{\AddDat{\TaddownTubeprime{1}}{N}{}}{}{} $
&$\AddDat{\AddDat{\TaddownTubeprime{1}}{N}{\dota}}{}{} $
\end{tabular}

\quad \quad \quad \quad

\begin{tabular}{ r  c c c }
&$\tilde{k}$&$\stackrel{\bullet}{\tilde{k}}$\\
\cline{2-3} 
&      &     \\[-2ex]
$\mor^B( e \ra \rho ) $ 
&$\AddDat{\AddDat{\TadupTube{1}}{B}{}}{}{} $
&$\AddDat{\AddDat{\TadupTube{1}}{B}{\dotc}}{}{} $\\
\\
$\mor^N(e \ra \rho ) $ 
&$\AddDat{\AddDat{\TadupTube{1}}{N}{}}{}{} $
&$\AddDat{\AddDat{\TadupTube{1}}{N}{\dotc}}{}{} $
\end{tabular}

}
\caption{\label{rhotoe} A complete basis of morphisms $\mor(\rho \ra e) \in  \tube(\halfesix/y) $ and $\mor(e \ra \rho) \in  \tube(\halfesix/y) $.
We have denoted these by $k$, $\stackrel{\bullet}{k}$ $\tilde{k}$, and $\stackrel{\bullet}{\tilde{k}}$.
}


\bigskip
\bigskip

\scalebox{0.86}{
\begin{tabular}{ r  c c c c c c c c }
&$v$&$t$&$X_{11}$&$X_{12}$&$\stackrel{\bullet}{v}$&$\stackrel{\bullet}{t}$&$\stackrel{\bullet}{X}_{11}$&$\stackrel{\bullet}{X}_{12}$ \\
\cline{2-9} 
&      &      &      &     &      &     &    &\\[-2ex]
$\mor^B(\rho \ra \rho) $ 
&$\AddDat{\vTube}{B}{} $
&$\AddDat{\tTube}{B}{} $
&$ \AddDat{\XTube{1}{1}}{B}{} $
&$ \AddDat{\XTube{1}{2}}{B}{}  $
&$\AddDat{\vTube}{B}{\dotb} $
&$\AddDat{\tTube}{B}{\dotc} $
&$ \AddDat{\XTube{1}{1}}{B}{\dotc} $
&$ \AddDat{\XTube{1}{2}}{B}{\dotc}$\\
\\
$\mor^N(\rho \ra \rho) $ 
&$\AddDat{\vTube}{N}{} $
&$\AddDat{\tTube}{N}{} $
&$ \AddDat{\XTube{1}{1}}{N}{} $
&$ \AddDat{\XTube{1}{2}}{N}{}  $
&$\AddDat{\vTube}{N}{\dotb} $
&$\AddDat{\tTube}{N}{\dotc} $
&$ \AddDat{\XTube{1}{1}}{N}{\dotc} $
&$ \AddDat{\XTube{1}{2}}{N}{\dotc}$\\
\end{tabular}
}
\caption{A complete basis of morphisms for $\mor(\rho \ra \rho) \in  \tube(\halfesix/y)$.
The labels above each tube are shorthand for that tube:
$v$ -- tube with vertical $\rho$ strand; 
$t$ -- tube with $\rho$ strand wrapping both cycles;
$X$ -- tube with all labels given by $\rho$. 
As before, a dot denotes an odd vector.}
\label{rhotorho}
\end{table}




In this subsection we compute bases for tube category morphism spaces. 
We will make use of the notation $s(X)$ defined in \eqref{sX_defn}.
Using the relations
\begin{align}
& \AddDat{\hTube}{X}{} \; =  s(X)  \AddDat{\hTube}{X}{} \quad \quad \quad \AddDat{\hTube}{X}{\dotb} \; =  -s(X)  \AddDat{\hTube}{X}{\dotb} 
\label{hlocalrelation}
\end{align}
we see that
a complete basis of morphisms from trivial (empty) boundary to the empty boundary is listed in Table \ref{etoe}. 
(The relations are found by taking two fermions out of the vacuum and sliding them around the annulus.)

Similarly, we have
\begin{align}
\AddDat{\TaddownTube{\mu }}{X}{}\;= s(X) \sigma^{x}_{\mu \nu} \AddDat{\TaddownTube{\nu}}{X}{} \quad \quad \quad
\AddDat{\TadupTube{\mu}}{X}{}\;= s(X) \sigma^y_{\mu \nu} \AddDat{\TadupTube{\nu}}{X}{}.
\end{align}
Hence some of these states are linearly dependent, and so a complete basis of morphisms is found if we fix the fusion space, 
and also consider the action of the odd endomorphism. 
The basis we choose is listed in Table \ref{rhotoe}.





The morphisms of $\text{mor}(\rho \ra \rho)$ satisfy
\begin{align}
& \AddDat{\XTube{\mu}{\nu}}{X}{} \;\;  =s(X) (\sigma^x \tp \sigma^y )_{\mu \nu; \kappa \tau}\AddDat{\XTube{\kappa}{\tau}}{X}{} 
\label{XlocalRelationAnnulus}
\end{align}
and also
\begin{align}
\AddDat{\XTube{\mu}{\nu}}{X}{\dotc} \;= (\sigma^y \tp \sigma^z)_{\mu \nu; \kappa \tau} \; \AddDat{\XTube{\kappa}{\tau}}{X}{\dota}
\end{align}
We can use these results to obtain a basis for $\text{mor}(\rho \ra \rho)$, which is given in Table \ref{rhotorho}.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Bases for tori} \label{TorusLocalRelations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this subsection we compute bases for the Hilbert spaces of spin tori.
We could of course do this using knowledge of tube category idempotents and \ref{torus_basis_theorem}, but
it's an instructive exercise to also compute bases using more elementary means.
In addition, when computing $S$ and $T$ matrices, it will be useful to have a topologically simple basis at our disposal.

\medskip

On the torus there are four spin structures.
We will first investigate the local relations on the three bounding tori which have spin structure $(X,Y) = (B,B),(N,B),(B,N)$.
Then we will consider the $(N,N)$ torus separately.
We use the same notation as in Section~\ref{modulartforms}. 

Depending on the spin structure, some of the annular tubes become zero after identifying the boundaries to form tori.
Since there is always one cycle with bounding spin structure, an odd tube is 
identified with zero for the same reason as discussed in \ref{c2_stringnets_torus}.
For another example, due to (\ref{hlocalrelation}) we have
\begin{align}
 0 = \;\AddDatTorus{\hTube}{N}{B} \;=\; \AddDatTorus{\vTube}{B}{N}\; = \; \AddDatTorus{\tTube}{B}{B}
\end{align}

We also get another local relation from \eqref{XlocalRelationAnnulus} after closing up the annulus to a torus, namely
\begin{align}
\AddDatTorus{\XTube{a}{b}}{X}{Y}{} \; = M_{ab;\alpha \beta} \AddDatTorus{\XTube{\alpha}{\beta}}{X}{Y}{} \qquad M = s(X) \sigma^x \tp \sigma^y, \; \; s(Y) \sigma^y \tp \sigma^z 
\end{align}
The two relations above can be multiplied to find a third:
\begin{align}
\AddDatTorus{\XTube{1}{1}}{X}{Y}{} \; = -s(X)s(Y) \AddDatTorus{\XTube{1}{2}}{X}{Y}{}  \; = -is(Y) \AddDatTorus{\XTube{2}{1}}{X}{Y}{} \; = -is(X) \AddDatTorus{\XTube{2}{2}}{X}{Y}{} 
\label{XLocalRelation}
\end{align}
We take the state with $(a,b) = (1,1)$ as the representative of this set of linearly dependent vectors. 

There is one additional useful linear relation to be found. 
This relation 
comes from nucleating a $\rho$ loop and extending it around the torus before fusing it back into the canonical basis:
\begin{align}
d_\rho \AddDatTorus{\eTube}{X}{Y} \; = \;
\AddDatTorus{\TorusLocalRelationa}{X}{Y} \;=\;
\AddDatTorus{\TorusLocalRelationb}{X}{Y} \;=\; 
\AddDatTorus{\TorusLocalRelationc}{X}{Y} \;=\; 
\sum_\lambda \; c_\lambda \AddDatTorus{\TorusNoLabelsx{\lambda}}{X}{Y},
\label{rhoLoopRelation}
\end{align}
where $c_\lambda$ are coefficients that depend on the $F$-symbols.
The string of equalities gives an additional local relation, in particular, it allows us 
solve for the tubes in (\ref{XLocalRelation}) above in terms of the other non-zero tubes.
Explicitly in the three sectors $(B,B), (B,N)$, and $(N,B)$ we have,
\begin{align}
& \AddDatTorus{\XTube{1}{1}}{B}{B} \;= e^{-i \pi /12} \frac{d+1}{\sqrt{d}} \left( \;\AddDatTorus{\eTube}{B}{B}\; -  \frac{1}{d} \left(\AddDatTorus{\hTube}{B}{B}   +  \AddDatTorus{\vTube}{B}{B}  \right) \right)\\
&\\
 & \AddDatTorus{\XTube{1}{1}}{B}{N} \; = e^{-5i \pi /12} \frac{d+1}{\sqrt{d}} \left( \AddDatTorus{\eTube}{B}{N} -  \frac{1}{d} \left( \AddDatTorus{\hTube}{B}{N}   + \AddDatTorus{\tTube}{B}{N} \right) \right)\\
 &\\
& \AddDatTorus{\XTube{1}{1}}{N}{B}  \;= e^{3 i \pi /4} \frac{d+1}{\sqrt{d}} \left( \AddDatTorus{\eTube}{N}{B}-  \frac{1}{d} \left( \AddDatTorus{\vTube}{N}{B} + \AddDatTorus{\tTube}{N}{B} \right) \right)
\end{align}

We now move on to the torus where the spin structure is non-bounding along both cycles.
We first notice that
\begin{align}
 0 = \;\AddDatTorus{\hTube}{N}{N} \;=\; \AddDatTorus{\vTube}{N}{N}\; = \; \AddDatTorus{\tTube}{N}{N}\;,
\end{align}
which can be seen by nucleating two fermions out of the vacuum along each $\rho$ line and 
dragging one of them along the entire $\rho$ line before fusing them back to the vacuum.
Furthermore, the same calculation as \eqref{rhoLoopRelation} implies that the empty tube is identified with zero:
\begin{align}
\AddDatTorus{\eTube}{N}{N} \; = 0
\end{align}
The only non-zero tube with even parity is given by
\begin{align}
\AddDatTorus{\XTube{1}{1}}{N}{N}
\end{align}
and those which are proportional to it are given by \eqref{XLocalRelation}. 

As one may expect from the Ising example, there are odd tubes which are non-zero.
Indeed we can find four of them,
\begin{align}
\AddDatTorusDot{\hTube}{N}{N}{\dotb}\quad \AddDatTorusDot{\vTube}{N}{N}{\dotb} \quad \AddDatTorusDot{\tTube}{N}{N}{\dotc} \quad \AddDatTorusDot{\XTube{1}{1}}{N}{N}{\dotc}.
\end{align}
However, these four tubes are not linearly independent. 
There are two independent linear relations that can be found between them by multiplying the tadpole-like diagrams in two different ways,
\begin{align}
\AddDatTorusDot{\TaddownTube{\mu}}{N}{N}{} \cdot \AddDatTorusDot{\TadupTube{\nu}}{N}{N}{\dotc} \;=\;
\AddDatTorusDot{\TadupTube{\nu}}{N}{N}{\dotc} \cdot  \AddDatTorusDot{\TaddownTube{\mu}}{N}{N}{} .
\end{align}
This is an instance of the familiar relation $cl(a\cdot b) = cl(b\cdot a)$.
Despite the indices $\mu$ and $\nu$ varying over four distinct values, this yields only two linearly independent relations on the torus. 
They are given by
\begin{align}
\frac{de^{ -i \pi / 4 }}{\sqrt{2}}  \AddDatTorusDot{\hTube}{N}{N}{\dotb}\; =\;
 \AddDatTorusDot{\vTube}{N}{N}{\dotb}  \; + \; 
 \AddDatTorusDot{\tTube}{N}{N}{\dotc} \; - \frac{2 e^{i \pi /4}}{\sqrt{d}}  
 \AddDatTorusDot{\XTube{1}{1}}{N}{N}{\dotc}
\end{align}
and\footnote{One can check that the second relation follows from the first by performing an $S$ transformation.}
\begin{align}
\frac{d e^{i \pi/4}}{\sqrt{2}}  \AddDatTorusDot{\vTube}{N}{N}{\dotb}\; = \;
\AddDatTorusDot{\hTube}{N}{N}{\dotb}\; + i 
 \AddDatTorusDot{\tTube}{N}{N}{\dotc}\; + \frac{2 e^{11i \pi /12}}{\sqrt{d}} 
 \AddDatTorusDot{\XTube{1}{1}}{N}{N}{\dotc}
\end{align}
We can now solve for any two of the above four states.
We choose
\begin{align}
 \AddDatTorusDot{\tTube}{N}{N}{\dotc}  \;&=\; \AddDatTorusDot{\hTube}{N}{N}{\dotb} \; -i\;  \AddDatTorusDot{\vTube}{N}{N}{\dotb}  \\
 &\\
 \AddDatTorusDot{\XTube{1}{1}}{N}{N}{\dotc} \;&=\;\sqrt{\frac{d}{2}}\left( e^{i \pi /3}\;  \AddDatTorusDot{\hTube}{N}{N}{\dotb} \; -i \; \AddDatTorusDot{\vTube}{N}{N}{\dotb} \;\right) 
\end{align}

In summary, the Hilbert spaces on each of the different spin tori are
\begin{align}
\begin{split}
A(T^2_{BB})  &\cong \mathbb{C}^{3|0} = \mathbb{C}\left[ \AddDatTorus{\eTube}{B}{B}{},\AddDatTorus{\hTube}{B}{B}{},\AddDatTorus{\vTube}{B}{B}{}\right]\\
&\\
A(T^2_{BN})  &\cong \mathbb{C}^{3|0}  = \mathbb{C}\left[\AddDatTorus{\eTube}{B}{N}{}, \AddDatTorus{\hTube}{B}{N}{}, \AddDatTorus{\tTube}{B}{N}{} \right]\\
&\\
A(T^2_{(NB})  &\cong \mathbb{C}^{3|0}=   \mathbb{C}\left[\AddDatTorus{\eTube}{N}{B}{}, \AddDatTorus{\vTube}{N}{B}{}, \AddDatTorus{\tTube}{N}{B}{} \right] \\
&\\
A(T^2_{NN})  &\cong \mathbb{C}^{1|2} = \mathbb{C} \left[ \AddDatTorusDot{\hTube}{N}{N}{\dotb}\;,\AddDatTorusDot{\tTube}{N}{N}{\dotc}\;,  \AddDatTorusDot{\XTube{1}{1}}{N}{N}{} \right]
\end{split}
\label{TorusBasis}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The tube category of $\halfesix / y$}   \label{he6mp-tube-cat}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this subsection we compute the minimal idempotents of the tube category of $\halfesix / y$. 
The tube category is somewhat exotic, 
and highlights many of the non-trivial features which arise when studying fermionic theories. 
We start by analyzing the idempotents from a purely algebraic point of view using only the dimensions of the morphism spaces, which can be inferred from Tables \ref{etoe}--\ref{rhotorho}.
We also provide explicit representations of the idempotents, which are given in Tables \ref{MIdempotentsprime} -- \ref{QIdempotents}.

\medskip

We begin by examining the bounding tube category. 
A basis for the morphism space $\mor^B(e \to e)$ is given in Table \ref{etoe}. 
As a vector space $\mor^B(e \to e)$ is isomorphic to $\cc^{2|0}$, 
and (as we have seen before in \eqref{C2etoe}) there is only one possible super algebra structure on $\cc^{2|0}$, given by $\cc \oplus \cc$.
(As before $\cc$ is shorthand for the trivial 1-dimensional algebra.)
Therefore this subcategory contains two inequivalent minimal idempotents. 
One is the trivial idempotent which we denote $m_1$, 
the other we denote $m_2$.
Explicit representations of these idempotents are given in Table \ref{MIdempotentsprime}. 
The trivial idempotent is the usual one, just given by the quantum dimensions. 
The non-trivial idempotent $m_2$ is easily computed from the constraint $m_1 + m_2 = \text{id}_{e}$ and is also listed in Table \ref{MIdempotentsprime}.

Next we look at $\mor^B(\rho \to e)$, 
a basis for which is listed in Table \ref{rhotoe}. 
As a vector space $\mor^B(\rho \to e ) \cong \cc^{1|1}$. 
This implies that $\mor^B(\rho \to \rho)$ contains a two by two matrix algebra $M(1|1)$.
One may think that it could just have easily been $Q(1)\oplus Q(1)$, 
but we know that the bounding tube category does not admit q-type simple objects; see the discussion at the end of Section \ref{ground_states_on_torus}.
Thus we find two minimal idempotents in $\mor^B(\rho \to \rho)$, both isomorphic to $m_2$ (they cannot be isomorphic to $m_1$ due to the no tadpole axiom.).
One of these minimal idempotents is evenly isomorphic to $m_2$ which we denote $m_2^+$, the other is oddly isomorphic and denoted $m_2^-$.
The two isomorphic idempotents are explicitly written in Table \ref{MIdempotents}.
(They are proportional to $k \cdot m_2\cdot  \tilde{k}$ and $\overset{\bullet}{k} \cdot m_2 \cdot \overset{\bullet}{\tilde{k}}$.)


We now look at $\mor^B(\rho \to \rho)$ and ask which part of it has not been accounted for. 
We see from Table \ref{rhotorho} that $\mor^B(\rho \to \rho) \cong \cc^{4|4}$ as a vector space. 
An $M(1|1)$ matrix algebra has been accounted for by $m_2^{\pm}$. 
Thus the only consistent super algebra structure is $\mor^B(\rho \to \rho) \cong M(1|1) \oplus M(1|1)$.
The remaining $M(1|1)$ contains two equivalent oddly isomorphic minimal idempotents, 
which we label as $m_3^+$ and $m_3^-$.


\medskip

The super algebra structure of the non-bounding tube category is more exotic but equally well tamed by the classification of semisimple super algebras.
We begin by looking at $\mor^N(e\to e) \cong \cc^{1|1}$. 
There is a unique simple algebra structure on $\cc^{1|1}$ given by $Q(1)$. 
We denote the corresponding q-type minimal idempotent by $q_1$.

Next we look at $\mor^N(e \to \rho)$ which is isomorphic to $\cc^{1|1}$ as a vector space. 
It follows that $\mor^N(\rho \to \rho)$ contains a $Q(1)$ summand, 
and a minimal idempotent isomorphic to $q_1$ which we denote $q_1'$, and list in Table \ref{QIdempotents}. 

We now turn to $\mor^N(\rho \to \rho) \cong \cc^{4|4}$. 
A $\cc^{1|1}$ dimensional subalgebra has been accounted for by $q_1$. 
Hence we only need to look at the complement of this subalgebra, which as a vector space is isomorphic to $\cc^{3|3}$.
There are two possible super algebra structures available: either three copies of $Q(1)$ or one copy of $Q(1)$ and one copy of $M(1|1)$.
However, $\tube^B$ and $\tube^N$ must contain the same number of non-isomorphic minimal idempotents, 
as shown at the end of Section \ref{ground_states_on_torus}. 
Since $\tube^B(\halfesix/y)$ has three non-isomorphic minimal idempotents, 
so must $\tube^N(\halfesix/y)$. 
Hence the algebra structure on the remaining $\cc^{3|3}$ must be $Q(1)\oplus M(1|1)$.
Correspondingly we find one q-type minimal idempotent which we label $q_2$, 
and two oddly isomorphic m-type minimal idempotents which we label $m_4^+$ and $m_4^-$.
These idempotents are given explicitly in Table \ref{QIdempotents}.


It is useful to write the isomorphisms between the idempotents in a standard form. 
Namely, if $e$ and $e'$ are isomorphic we can write $ e = u \cdot v$ and $e' = v \cdot u$ for some $u$ and $v$. 
In an obvious notation we have,
\begin{align}
m_2 = \frac{e^{i \pi /4}}{2} \sqrt{\frac{d}{3}} \AddDatTorusDot{\TaddownTube{1}}{B}{}{}  \cdot  \AddDatTorusDot{\TadupTube{1}}{B}{}{}  \; = \frac{e^{- i \pi /4}}{2} \sqrt{\frac{d}{3}} \AddDatTorusDot{\TaddownTube{1}}{B}{}{\dota} \cdot \AddDatTorusDot{\TadupTube{1}}{B}{}{\dotc} 
\end{align}
which can be used to track the isomorphisms across the three representatives $m_2$, $m_2^+$ and $m_2^-$.
Similarly we have,
\begin{align}
q_1 = \frac{e^{i \pi/4}}{\sqrt{d}} \AddDatTorusDot{\TaddownTube{1}}{N}{}{}  \cdot  \AddDatTorusDot{\TadupTube{1}}{N}{}{} .
\end{align}
Lastly we note that $m_3^+ \cdot \overset{\bullet}{v}  = \overset{\bullet}{v}  \cdot m_3^-$, and $m_4^+ \cdot \overset{\bullet}{v}  = \overset{\bullet}{v}  \cdot m_4^-$ where $\overset{\bullet}{v} $ is listed in Table \ref{rhotorho}.
Consequently we have,
\begin{align}
m_3^+ = \lambda^{-1}(m_3^+ \cdot \overset{\bullet}{v} ) \cdot (\overset{\bullet}{v}  \cdot m_3^+) \quad \quad \quad m_3^- = \lambda^{-1}(\overset{\bullet}{v}  \cdot m_3^+) \cdot  (m_3^+ \cdot \overset{\bullet}{v} )
\end{align}
and similarly, 
\begin{align}
m_4^+ = \lambda^{-1}(m_4^+ \cdot \overset{\bullet}{v} ) \cdot (\overset{\bullet}{v}  \cdot m_4^+) \quad \quad \quad m_4^- = \lambda^{-1}(\overset{\bullet}{v}  \cdot m_4^+) \cdot  (m_4^+ \cdot \overset{\bullet}{v} ).
\end{align}

The twists and quantum dimensions of the idempotents can be computed with the techniques developed 
in previous sections; we list the results in Table \ref{TubehalfesixQD}.
 
We also note that an idempotent of the parent tube category can always be included into the tube category of the condensed theory.
As in Section \ref{mtc_idem_subsect} the inclusion can be non-trivial: some of the idempotents may become isomorphic, or even equal to zero.
In Appendix \ref{IdempotentsHalfESix}, we compute the minimal idempotents of $\tube(\halfesix)$ and track their images under the inclusion into $\tube(\halfesix/y)$. 
This also provides an additional crosscheck on the minimal idempotents given in tables \ref{MIdempotentsprime} -- \ref{QIdempotents}.





\begin{table}
\centering
{{\tabulinesep=1.2mm
\begin{tabular}{ c c | c c }
type &twist & $\AddDat{\eTube}{B}{}$ & $\AddDat{\hTube}{B}{}$ \\ \hline
${m}_{1}$ &$1$ & $\frac{1}{d \sqrt{3}}$ & $\frac{1}{2 \sqrt{3}}$\\ \hline
${m}_{2}$&$1$ & $ \frac{d}{2 \sqrt{3}}$ & $\frac{-1}{2 \sqrt{3}}$ 
\end{tabular}
}}
\caption{
\label{MIdempotentsprime}
Quasiparticles of $\halfesix$ with bounding spin structure and trivial boundary condition.
The particle is a linear combination of the tubes shown at the top of the table multipled by the coefficients in the row.}
\end{table}

\begin{table}
\centering
{\tabulinesep=1.2mm
\begin{tabular}{ c c | c c c c }
type &twist &  $\AddDat{\vTube}{B}{} $ & $\AddDat{\tTube}{B}{} $ & $\AddDat{\XTube{1}{1}}{B}{} $ & $\AddDat{\XTube{1}{2}}{B}{} $ \\ \hline
${m}_{2}^+$&$1$ & $\frac{1}{2 \sqrt{3}}$  & $\frac{1}{2 \sqrt{3}}$  & $\frac{e^{i \pi /4}}{2 \sqrt{d}}$ & $\frac{- e^{-i \pi/4} }{2 \sqrt{3d}}$ \\
${m}_2^{-}$&$-1$  & $\frac{1}{2 \sqrt{3}}$  & $\frac{-1}{2 \sqrt{3}}$  &  $\frac{ e^{-i \pi/4} }{2 \sqrt{3d}}$& $\frac{-e^{i \pi /4}}{2 \sqrt{d}}$ \\ \hline
${m}_3^+$&$e^{i \pi /3}$  & $\frac{1}{2 + d}$ & $\frac{e^{- i \pi /3}}{2+d}$ & $\frac{- e^{i \pi /12}}{\sqrt{3d}}$ &  \\
${m}_3^-$&$-e^{i \pi /3}$  & $\frac{1}{2 + d}$ & $\frac{-e^{- i \pi /3}}{2+d} $&  & $\frac{e^{i \pi /12}}{\sqrt{3d}}$  \\ 
\end{tabular}
}
\caption{\label{MIdempotents} Quasiparticles of $\halfesix$ with bounding spin structures, and boundary condition $\rho$.
The tube with a single $\rho$ line is a direct sum of four simple objects, 
two of which we name $m_2^+$ and $m_3^+$.
The other two are oddly isomorphic to $m_2^+$ and $m_3^+$, 
and we denote them $m_2^-$ and $m_3^-$ 
}
\end{table}

\begin{table}
{{\tabulinesep=1.2mm
\begin{tabular}{ c c | c }
type& twist & $\AddDat{\eTube}{N}{}$ \\ \hline
${q}_{1}$ &$1$&1
\end{tabular}
}
$\qquad$
{\tabulinesep=1.2mm
\begin{tabular}{c  c | c c c c }
type& twist & $\AddDat{\vTube}{N}{}$ & $\AddDat{\tTube}{N}{}$  & $\AddDat{\XTube{1}{1}}{N}{}$ & $\AddDat{\XTube{1}{2}}{N}{}$ \\ \hline
${q}_1'$&$1$ & $ \frac{1}{d}$&$ \frac{1}{d} $& $\frac{- e^{i \pi/4}}{d\sqrt{d}}$ & $\frac{- e^{i \pi/4}}{d\sqrt{d}}$ \\ \hline
${q}_2$&$-i$ &$ \frac{1}{2+d} $& $\frac{i}{2+d}$ & $\frac{i \gamma}{\sqrt{2+d}}$ & $\frac{i \gamma}{\sqrt{2+d}}$ \\ \hline 
${m}_4^+$&$e^{5i \pi/6}$&$ \frac{1}{2+d} $&$ \frac{e^{-5i\pi/6}}{2+d} $ & $\frac{- \alpha e^{5 i \pi/6}}{\sqrt{2+d}}$ & $\frac{\beta e^{5 i \pi /6}}{\sqrt{2+d}}$ \\ 
${m}_4^-$&$e^{5i \pi/6}$&$ \frac{1}{2+d} $&$ \frac{e^{-5i\pi/6}}{2+d} $ &  $\frac{\beta e^{5 i \pi /6}}{\sqrt{2+d}}$  &$\frac{- \alpha e^{5 i \pi/6}}{\sqrt{2+d}}$ 
\end{tabular}
 }
\caption{  \label{QIdempotents} Quasiparticles of $\frac{1}{2} E6$ with vortex (periodic) spin structures. Two are q-type, and one is m-type. The m-type particle is two-dimensional, consisting of of two smaller simple modules.  $\Pi$ is an odd isomorphism, and 
$\alpha = \frac{1}{2} \left( 1+ 1/\sqrt{2d+1} \right)$, and $\beta = \frac{1}{2} \left( 1- 1/\sqrt{2d+1} \right)$. 
}}
\end{table}

\begin{table}
\begin{flalign*} & \begin{array}{r@{ \quad \quad \quad}  c @{\quad \quad} c @{\quad \quad} c @{\quad \quad \quad \quad } c  @{\quad \quad} c @{\quad \quad} c  }
			\text{particle}				&m_1		&m_2		&m_3^+	&q_1	&q_2	&m_4 \\[.5ex] \hline \\ [-2ex]
			\text{quantum dimension}		&1			&1+d		&d		&2+d	&d		&d\\ [.5ex]
			\text{twist}				&1			&1		&e^{- i \pi/3}	&1	&i	&e^{-5 i \pi /6} \\
						\end{array} & \end{flalign*}
	\caption{The $\halfesix$ quantum dimensions and twists. 
	We have normalized the quantum dimensions by the quantum dimension of the trivial idempotent. 
	 The total quantum dimension is given by $\mcd = d\sqrt{6}$.}
	\label{TubehalfesixQD}
\end{table}

\medskip

The fusion rules in the condensed theory can be calculated using \eqref{PplusQ} and \eqref{PminusQ} as well as the S-matrix which we compute in the next section. 
We list the fusion rules in Table \ref{TubehalfesixFusionRules}. 
A particularly noteworthy fusion rule is:
\begin{align}
m_4^+ \tp m_4^+ \cong \cc^{0|1} m_1 \oplus m_2 \oplus m_3^+.
\end{align}
The odd vector space coefficient of the trivial object $m_1$ implies that $m_4^+$ is oddly self dual. 
Let's show explicitly that $\mor(\unit \ra m_4^+ \tp m_4^+) \cong \cc^{0|1}$.
We first note the following linear relations,
\begin{align}
\label{sphericity_for_twist}
\underset{m_\unit}{\Pantsmsixa} &= \underset{m_\unit}{\Pantsmsixb}\\
\label{sphericity_for_twistprime}
\underset{m_\unit}{\Pantsmsixc} &= \sum_{\alpha \beta} P_{a\alpha} (P^2)_{b \beta} \underset{m_\unit}{\Pantsmsixd}.
\end{align}
The boundary is labeled by $m_\unit$ and allows us to treat the pair of pants 
as if it were a sphere with two disks removed each with one marked point labeled $\rho$.
Indeed \eqref{sphericity_for_twist} follows directly from this observation, while \eqref{sphericity_for_twistprime} also requires some pivots. 
After plugging in the coefficients and using \eqref{XlocalRelationAnnulus}, one finds that
\begin{align}
\underset{m_\unit}{\Pantsmsixe} &= \underset{m_\unit}{\Pantsmsixh}  \\
\underset{m_\unit}{\Pantsmsixf} &= \underset{m_\unit}{ \Pantsmsixg}.
\end{align}
Under interchanging $X_{11}$ with $X_{12}$, we see that $m_4^+$ is interchanged with $m_4^-$. 
It follows that inserting the $m_4^+$ idempotent on the right hand side of the pair of pants is equivalent to inserting $m_4^-$ on the left hand side of the pair of pants.
Using that $\overset{\bullet}{v}\cdot  m_4^- = m_4^+ \cdot \overset{\bullet}{v}$, a basis for $V^{m_4^+ m_4^+}_\unit$ is generated by a single odd vector:
\begin{align}
\nonumber
V^{m_4^+ m_4^+}_\unit =   
&\left \langle \underset{m_\unit}{\Vmsixa}
+e^{-5 i \pi /6} \underset{m_\unit}{\Vmsixb} \right. \\ 
-& \left. \alpha \sqrt{2+d}  e^{5 i \pi /6}\underset{m_\unit}{\Vmsixc}
+\beta \sqrt{2 + d} e^{5 i \pi /6} \underset{m_\unit}{\Vmsixd}
\right \rangle,
\end{align}
and so $V^{m_4^+ m_4^+}_\unit \cong \cc^{0|1}$. 


			\begin{table}
\begin{flalign*} & \begin{array}{c@{ \quad}  | @{\quad \quad} l @{\quad \quad} l @{\quad \quad} l}
			\mca \tp \mca 		&m_1		&m_2		&m_3^+		\\[.5ex] \hline \\ [-2ex]
			m_1		 		&m_1		&m_2		&m_3^+		\\
			m_2		 		&m_2		&m_1\oplus \cc^{1|1}m_2	\oplus \cc^{1|1}m_3^+	&\cc^{1|1}  m_2 \oplus \cc^{0|1}m_3^+		\\
			m_3^+		 		&m_3^+		&\cc^{1|1} m_2 \oplus \cc^{0|1}m_3^+		&m_1 \oplus \cc^{0|1}m_2 \oplus m_3^+		\\
			\end{array} & \end{flalign*}
	
\begin{flalign*} & \begin{array}{c@{ \quad}  | @{\quad \quad} l @{\quad \quad} l @{\quad \quad} l}
			\mcv \tp \mca 		&m_1		&m_2									&m_3^+		\\[.5ex] \hline \\ [-2ex]
			q_1				&q_1		&\cc^{1|1}q_1 \oplus q_2 \oplus \cc^{1|1}m_4^+		&q_1 \oplus q_2 \oplus \cc^{1|1}m_4^+		\\
			q_2				&q_2		&q_1 \oplus \cc^{1|1} m_4^+					&q_1 \oplus  q_2		\\
			m_4^+		 		&m_4^+		&q_1 \oplus q_2 \oplus \cc^{0|1}m_4^+			&q_1 \oplus \cc^{0|1} m_4^+		\\
			\end{array} & \end{flalign*}		

\begin{flalign*} & \begin{array}{c@{ \quad}  | @{\quad \quad} l @{\quad \quad} l @{\quad \quad} l}
			\mcv \tp \mcv 		&q_1		&q_2		&m_4^+		\\[.5ex] \hline \\ [-2ex]
			q_1		 		&\cc^{1|1}m_1\oplus \cc^{2|2} m_2 \oplus \cc^{1|1}m_3^+		&\cc^{1|1}m_2 \oplus \cc^{1|1}m_3^+		&\cc^{1|1}m_2 \oplus \cc^{1|1}m_3^+		\\
			q_2		 		&\cc^{1|1}m_2 \oplus \cc^{1|1}m_3^+		&\cc^{1|1}m_1 \oplus m_3^+		&\cc^{1|1}m_2		\\
			m_4^+		 		&\cc^{1|1}m_2 \oplus \cc^{1|1}m_3^+ 		&\cc^{1|1}m_2 		&\text{\textcolor{red}{$\cc^{0|1}$}}m_1 \oplus m_2 \oplus m_3^+		\\
			\end{array} & \end{flalign*}
	\caption{ \label{TubehalfesixFusionRules} 
$\halfesix$ fusion rules. We define $\mca = \{ m_1, m_2, m_3^+\}$ and $\mcv = \{ q_1, q_2, m_4^+ \}$ as the set of non-vortex and vortex quasiparticles, respectively. 
	The $\cc^{p|q}$ denote the vector space associated with $\Delta^{ab}_c$ which is related to the fusion space through $V^{ab}_c =\Delta^{ab}_c \tp \text{End}(c)$.
	Notice that $m_4^+$ is oddly self-dual (the relevant fusion channel is marked in red), and hence it has a Frobenius-Schur indicator of $\pm i$.
			} 
\end{table}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Modular transformations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Topological and idempotent bases}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
There are two natural bases on the torus. 
One is the topological basis, corresponding to (\ref{TorusBasis}), the other is the 
idempotent basis (or quasiparticle basis) given in Tables \ref{MIdempotents} and \ref{QIdempotents}.
We will compute the modular transformations in the topological basis first, and then change over to the idempotent basis.

We define the shorthand notation for the tubes as in Tables \ref{etoe}--\ref{rhotorho}
We will then denote the spin structure by a subscript, for example,
\begin{align}
h_{BN} =\; \AddDatTorus{\hTube}{B}{N}{}
\end{align}




Every state on the torus can be expanded in terms of the above states, as long 
as we are also careful to use the relations provided in Section \ref{TorusLocalRelations}.
Hence one can directly compute the change of basis by taking the particles in 
Tables \ref{MIdempotentsprime}, \ref{MIdempotents},  and \ref{QIdempotents} and 
projecting them onto the torus, and then modding out by the relations described in Section \ref{TorusLocalRelations}.
The change of basis matrices in the spin sectors with at least one bounding cycle are 
\begin{align}
\label{VAA}
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BB} 
&= \left( \begin{matrix}
\frac{1}{d\sqrt{3}} & 0 & \frac{1}{2 \sqrt{3}} \\
\frac{d}{2 \sqrt{3}} & 0 & - \frac{1}{2 \sqrt{3}} \\
- \frac{d}{2 \sqrt{3}} & \frac{1}{2} & \frac{1}{2 \sqrt{3}}
\end{matrix} \right)
\left( \begin{matrix}
e\\
v\\
h\\
\end{matrix} \right)_{BB}\\
\label{VAP}  
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BN}
&= \left( \begin{matrix}
\frac{1}{d\sqrt{3}} & 0 & \frac{1}{2 \sqrt{3}} \\
\frac{d}{2 \sqrt{3}} & 0 & - \frac{1}{2 \sqrt{3}} \\
\frac{d e^{2 \pi i/3}}{2 \sqrt{3}} & \frac{e^{- i \pi /3}}{2} & \frac{e^{- i \pi /3}}{2 \sqrt{3}}\\
\end{matrix} \right)
\left( \begin{matrix}
e\\
t\\
h\\
\end{matrix} \right)_{BN} \\
\label{VPA} 
\left( \begin{matrix}
{q}_1\\
{q}_2\\
m_4^+\\
\end{matrix} \right)_{NB}
&= \left( \begin{matrix}
1 & 0 & 0 \\
\sqrt{\frac{1+d}{3}} e^{-3i \pi /4} & \frac{e^{i \pi /6}}{\sqrt{3}} & \frac{e^{i \pi /3}}{\sqrt{3}} \\
\frac{e^{7 i \pi /12}}{\sqrt{6}} & \frac{e^{- i \pi / 6}}{2 \sqrt{3}} & \frac{e^{-2 i \pi /3}}{2 \sqrt{3}}\\
\end{matrix} \right)
\left( \begin{matrix}
e\\
v\\
t\\
\end{matrix} \right)_{NB} \\
\end{align}

For the non-bounding $NN$ spin structure the q-type idempotents need to be closed up into a torus with an odd isomorphism
We define $\left[ \stackrel{\bullet}{q}_{i}\right]^2  = q_i$. 
This has a $\pm$ ambiguity, we denote the $\pm$ signs by $\sigma_i$. 
We can also change to the idempotent basis with,
\begin{align}
\label{VPP}
\left( \begin{matrix}
\stackrel{\bullet}{q}_{1}\\
\stackrel{\bullet}{q}_{2}\\
m_4^+ \\ 
\end{matrix} \right) \; =\;
\left( \begin{matrix}
\sigma_1 e^{- i \pi /4} &0&0\\
0&\sigma_2 e^{- i \pi /4} &0\\
0&0&1 \\
\end{matrix} \right)
\left( \begin{matrix}
\frac{e^{- i \pi /4}}{\sqrt{2}} & 0&0 \\
- \frac{e^{- i \pi /4}}{\sqrt{2}} & 1 & 0 \\
0 & 0& - \frac{e^{5 i \pi /6}}{\sqrt{2 + d}}\\
\end{matrix} \right)
\left( \begin{matrix}
\stackrel{\bullet}{h} \\
\stackrel{\bullet}{v} \\
X \\
\end{matrix} \right)
\end{align}

The q-type idempotents have norm square of $2$ (due to their two-dimensional endomorphism algebras), 
as opposed to the m-type idempotents that have norm square of $1$. 
To ensure that the modular matrices are unitary, we adjust for this by defining $\widehat{q} = q/\sqrt{2}$. 
When written in terms of the $\widehat{q}$, the modular matrices are unitary. 


%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$S$ transformation}
\label{E6S_matrix_section}
%%%%%%%%%%%%%%%%%%%%%%

The $S$ transformation exchanges the longitudinal and meridional cycles of the torus.
Since we are drawing the tori as annuli with their boundaries identified, the $S$ transformation looks like
\begin{align}
\xymatrix @!0 @M=1mm  @C=20mm{
S^{XY \rightarrow \widetilde{X}\widetilde{Y}}:& A(T^2_{XY}) \ar[rr] &&A(T^2_{\widetilde{X}\widetilde{Y}}) & \\
&&&&\\
& \AnnularTubex{\AnnularTubeNoIndex}{}{}{\psi}{X}{Y}\ar@{|->}[rr] &&\SAnnulusx{\psi}{\widetilde{X}}{\widetilde{Y}}\; & 
 }
 \label{STopologicalBasis}
\end{align}
with the transformed spin structure $\widetilde{X}\widetilde{Y}$ being found with the aid of Figure  \ref{spin_str_mapping_class_group}. 
In terms of the matrix elements of $S$, we have
\begin{align}
\SAnnulusx{\psi}{\widetilde{X}}{\widetilde{Y}} \;= \sum_{\lambda \in A(T^2,\widetilde{X}\widetilde{Y})}  S^{XY \rightarrow \widetilde{X}\widetilde{Y}}_{\psi \lambda} \AnnularTubex{\AnnularTubeNoIndex}{}{}{\lambda}{\widetilde{X}}{\widetilde{Y}} \\
\end{align}
Where we have taken $\psi,\lambda  \in \bigoplus_{ab} V^{aba^*}_b$ modulo local relations.

We can now work out the $S$-matrix for each spin structure in the topological basis, and then change over to the idempotent basis. 
The calculation is the same in each case, we find the linear map on the 
topological basis based on (\ref{STopologicalBasis}), and then change back to the particle basis using (\ref{VPA}--\ref{VPP}).

For the $BB$ spin structure one simply finds that $v$ and $h$ are interchanged so that,
\begin{align}
\left( \begin{matrix}
e\\
v\\
h\\
\end{matrix} \right)_{BB}
\xrightarrow{S^{BB \rightarrow BB}}
\left(\begin{matrix}
1& 0& 0 \\
0& 0&1  \\
0&1 &0 \\ 
\end{matrix} \right)
\left( \begin{matrix}
e\\
v\\
h\\
\end{matrix} \right)_{BB}
\end{align}
We can now write down the $S$-matrix in the idempotent basis using the change of basis in (\ref{VAA})
\begin{align}
\left( \begin{matrix}
m_1\\
m_2\\
m_3^+\\
\end{matrix} \right)_{BB} \xrightarrow{S^{BB \rightarrow BB}} 
\frac{1}{\sqrt{3}}\left( \begin{matrix}
\frac{1}{d} & \frac{d}{2} & 1\\ 
\frac{d}{2} & \frac{1}{d} & -1\\
1 & -1 & 1\\
\end{matrix} \right)
\left( \begin{matrix}
m_1\\
m_2\\
m_3^+\\
\end{matrix} \right)_{BB}
\end{align}

Next we compute the $S$-matrix elements that transition between the $BN$ and $NB$ tori.
We first find the action of S on the $BN$ torus:
\begin{align}
\left( \begin{matrix}
e\\
h\\
v\\
\end{matrix} \right)_{BN} 
 \xrightarrow{S^{BN\rightarrow NB}}
\left( \begin{matrix}
1&0&0\\
0&1&0\\
d e^{-i \pi/6} & e^{5 i \pi/6}  & e^{2 \pi i /3}\\
\end{matrix} \right)
\left( \begin{matrix}
e\\
v\\
t\\
\end{matrix} \right)_{NB}
\end{align}
which can be written in the idempotent basis as
\begin{align}\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BN}
\xrightarrow{S^{BN \rightarrow NB}}
\left( \begin{matrix}
\frac{1}{2} & \frac{1}{2 \sqrt{3}} &  \frac{1}{\sqrt{3}} \\
\frac{1}{2} & - \frac{1}{2\sqrt{3}} & -\frac{1}{\sqrt{3}} \\
0& \frac{1}{\sqrt{3}} & -\frac{1}{\sqrt{3}} \\
\end{matrix} \right)
\left( \begin{matrix}
{q}_1\\
{q}_2\\
m_4^+\\
\end{matrix} \right)_{NB}.
\end{align}
Similarly we can work out the $S$-matrix in the topological basis for the $(N,B)$ torus,
\begin{align}
\left( \begin{matrix}
e \\ 
v\\ 
t\\ 
\end{matrix} \right)_{NB}
  \xrightarrow{S^{NB \rightarrow BN}}
\left( \begin{matrix}
1&0&0\\
0&1&0\\
de^{i \pi/6} & e^{-5 i \pi /6} & e^{-2 i \pi /3}
\end{matrix} \right)
\left( \begin{matrix}
e \\
h\\ 
t\\ 
\end{matrix} \right)_{BN} 
\end{align}
And again we can write this in the idempotent basis:
\begin{align}
\left( \begin{matrix}
{q}_1\\
{q}_2\\
m_4^+\\
\end{matrix} \right)_{NB}
\xrightarrow{S^{NB \rightarrow BN}}
\left( \begin{matrix}
1& 1& 0 \\
\frac{1}{\sqrt{3}} & - \frac{1}{\sqrt{3}} & \frac{2}{\sqrt{3}} \\
\frac{1}{\sqrt{3}} & - \frac{1}{\sqrt{3}} & - \frac{1}{\sqrt{3}} \\
\end{matrix} \right)
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BN}
\end{align}
Notice that the $S$-matrix is invertible, but not unitary. 
This is because we didn't normalize our idempotents appropriately. 
As mentioned earlier, we write the normalized $Q$ idempotents with a hat, $\widehat{Q}_i = Q_i /\sqrt{2}$.
Once doing so we find the appropriately normalized $S$-matrix is given by
\begin{align}\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BN}
\xrightarrow{S^{BN \rightarrow NB}}
\left( \begin{matrix}
\frac{1}{\sqrt{2}} & \frac{1}{\sqrt{6}} &  \frac{1}{\sqrt{3}} \\
\frac{1}{\sqrt{2}} & - \frac{1}{\sqrt{6}} & -\frac{1}{\sqrt{3}} \\
0& \sqrt{\frac{2}{3}} & -\frac{1}{\sqrt{3}} \\
\end{matrix} \right)
\left( \begin{matrix}
\widehat{{q}}_1\\
\widehat{{q}}_2\\
m_4^+\\
\end{matrix} \right)_{NB}
\end{align}
\begin{align}
\left( \begin{matrix}
\widehat{{q}}_1\\
\widehat{{q}}_2\\
m_4^+\\
\end{matrix} \right)_{NB}
\xrightarrow{S^{NB \rightarrow BN}}
\left( \begin{matrix}
\frac{1}{\sqrt{2}}& \frac{1}{\sqrt{2}}& 0 \\
\frac{1}{\sqrt{6}} & - \frac{1}{\sqrt{6}} & \sqrt{\frac{2}{3}} \\
\frac{1}{\sqrt{3}} & - \frac{1}{\sqrt{3}} & - \frac{1}{\sqrt{3}} \\
\end{matrix} \right)
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BN}
\end{align}
Notice that the matrix is symmetric, and unitary.

Lastly, we can work out the $S$-matrix on the non-bounding torus.
\begin{align}
\left( \begin{matrix}
\stackrel{\bullet}{h} \\
\stackrel{\bullet}{v} \\
X \\
\end{matrix} \right)_{NN}
\xrightarrow{S^{NN\rightarrow NN}} 
\left( \begin{matrix}
0&i  &0 \\ 
1&0 &0 \\
0&0& -i \\
\end{matrix} \right)
\left( \begin{matrix}
\stackrel{\bullet}{h} \\
\stackrel{\bullet}{v} \\
X \\\end{matrix} \right)_{NN}
\end{align}
In the idempotent basis, this is
\begin{align}   \label{hE6_S_NN}
\left( \begin{matrix}
\stackrel{\bullet}{q}_{1}\\
\stackrel{\bullet}{q}_{2}\\
m_4^+ \\ 
\end{matrix} \right)_{NN}
 \xrightarrow{S^{NN \rightarrow NN}}
\frac{e^{i \pi /4}}{\sqrt{2}}\left( \begin{matrix} 
1&\Sigma &0 \\
\Sigma &-1&0\\
0&0& -\sqrt{2} e^{i \pi /4}\\
\end{matrix} \right)
\left( \begin{matrix}
\stackrel{\bullet}{q}_{1}\\
\stackrel{\bullet}{q}_{2}\\
m_4^+ \\ 
\end{matrix} \right)_{NN}
\quad \quad \text{where $\Sigma = \sigma_1 \sigma_2$.}
\end{align}
Note that $S^{NN\ra NN}$ splits as $S^{NN\ra NN}_q \oplus S^{NN\ra NN}_m$ into blocks which operate 
on q-type and m-type particles, as it must: 
the basis vectors coming from m-type (q-type) idempotents are even (odd), and $S$ preserves fermion parity.

In summary, we have \eqref{hE6_S_NN} together with 
\begin{align}
\left(\begin{matrix}
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BN} \\
\\
\left( \begin{matrix}
\widehat{{q}}_1\\
\widehat{{q}}_2\\
m_4^+\\
\end{matrix} \right)_{NB}\\
\\
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BB} \\
\end{matrix} \right)
\xrightarrow{S} \left( \begin{matrix}
&&&			\frac{1}{\sqrt{2}} & \frac{1}{\sqrt{6}} &  \frac{1}{\sqrt{3}} &			&&\\
&&&			\frac{1}{\sqrt{2}} & - \frac{1}{\sqrt{6}} & -\frac{1}{\sqrt{3}}& 			&&\\
&&&			0& \sqrt{\frac{2}{3}} & -\frac{1}{\sqrt{3}}& 			&&\\
\frac{1}{\sqrt{2}}& \frac{1}{\sqrt{2}}& 0&			&&& 			&&\\
\frac{1}{\sqrt{6}} & - \frac{1}{\sqrt{6}} & \sqrt{\frac{2}{3}}&			&&& 			&&\\
\frac{1}{\sqrt{3}} & - \frac{1}{\sqrt{3}} & - \frac{1}{\sqrt{3}}&			&&& 			&&\\
&&&			&&&			\frac{1}{d\sqrt{3}} & \frac{d}{2\sqrt{3}} & \frac{1}{\sqrt{3}}\\
&&&			&&& 			\frac{d}{2\sqrt{3}} & \frac{1}{d\sqrt{3}} & -\frac{1}{\sqrt{3}}\\
&&&			&&& 			\frac{1}{\sqrt{3}} & -\frac{1}{\sqrt{3}} & \frac{1}{\sqrt{3}}\\
\end{matrix} \right)
\left(\begin{matrix}
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BN} \\
\\
\left( \begin{matrix}
\widehat{{q}}_1\\
\widehat{{q}}_2\\
m_4^+\\
\end{matrix} \right)_{NB}\\
\\
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BB} \\
\end{matrix} \right)
\end{align}


%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$T$ transformation}
%%%%%%%%%%%%%%%%%%%%%%%

The Dehn twist ($T$-transformation) corresponds to cutting the torus open along one cycle, 
applying a full $2\pi$ rotation and then gluing the torus back together along that cycle.
\begin{align}
\xymatrix @!0 @M=1mm  @C=20mm{
T^{XY \rightarrow \widetilde{X}\widetilde{Y}}:& A(T^2_{XY}) \ar[rr] &&A(T^2_{\widetilde{X}\widetilde{Y}}) & \\
&&&&\\
& \AnnularTubex{\AnnularTubeNoIndex}{}{}{\psi}{X}{Y}\ar@{|->}[rr] &&\TAnnulusx{\psi}{\widetilde{X}}{\widetilde{Y}}\; & 
 }
 \label{TTopologicalBasis}
\end{align}
with the spin structure transforming according to Figure \ref{spin_str_mapping_class_group}. 
In terms of the matrix elements of $T$, 
\begin{align}
\TAnnulusx{\psi}{\widetilde{X}}{\widetilde{Y}} \;= \sum_{\lambda \in A(T^2_{\widetilde{X}\widetilde{Y}})}  T^{XY \rightarrow \widetilde{X}\widetilde{Y}}_{\psi \lambda} \AnnularTubex{\AnnularTubeNoIndex}{}{}{\lambda}{\widetilde{X}}{\widetilde{Y}}.
\end{align}

Aside from spin structure considerations, all idempotents are eigenstates of the Dehn twist,
with $T$ acting diagonally within each spin-structure block. 




To find the eigenvalues, we compute the Dehn twist in the topological basis and then change back to the idempotent basis as usual. 
We find
\begin{align}
\left( \begin{matrix}
\stackrel{\bullet}{q}_{1}\\
\stackrel{\bullet}{q}_{2}\\
m_4^+ \\ 
\end{matrix} \right)_{NN} \xrightarrow{T^{NN\rightarrow NN}}
\left( \begin{matrix} 
1 & 0&0 \\
0 & -i & 0 \\
0 & 0& e^{5 i \pi /6}\\
\end{matrix} \right) 
\left( \begin{matrix}
\stackrel{\bullet}{q}_{1}\\
\stackrel{\bullet}{q}_{2}\\
m_4^+ \\ 
\end{matrix} \right)_{NN}
\end{align}
for the $NN$ torus, and 
\begin{align}
\left(\begin{matrix}
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BN} \\
\\
\left( \begin{matrix}
\widehat{{q}}_1\\
\widehat{{q}}_2\\
m_4^+\\
\end{matrix} \right)_{NB}\\
\\
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BB} \\
\end{matrix} \right)
\xrightarrow{T} \left( \begin{matrix}
&&&			&&&			1&0&0	\\
&&&			&&&			0&1&0	\\
&&&			&&&			0&0&e^{i \pi/3}	\\
&&&			1&0&0&			&&	\\
&&&			0&-i&0&			&&	\\
&&&			0&0&e^{5 i \pi /6}&			&&	\\
1&0&0&			&&&			&&	\\
0&1&0&			&&&			&&	\\
0&0&e^{i \pi /3}&			&&&			&&	\\		
\end{matrix} \right)
\left(\begin{matrix}
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BN} \\
\\
\left( \begin{matrix}
\widehat{{q}}_1\\
\widehat{{q}}_2\\
m_4^+\\
\end{matrix} \right)_{NB}\\
\\
\left( \begin{matrix}
{m}_1\\
{m}_2\\
m_3^+\\
\end{matrix} \right)_{BB} \\
\end{matrix} \right)
\end{align}
for the spin tori with at least one bounding cycle.
One can check that the modular matrices defined above satisfy $S^4 = (-1)^F$ and $(ST)^3 = (-1)^F$. 



