%auto-ignore
%      this ensures the arxiv doesn't try to start TeXing here.
%!TEX root = super_lattice_models_draft.tex
%      prev line helps TeXShop do the right thing

%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%

A large program in condensed matter physics in recent years has been to classify 
topological phases of matter which host emergent quasiparticle excitations 
with topological properties, like exotic braiding statistics. 
The mathematical framework of category theory has proven to provide the right 
framework needed to formally develop classification efforts. 
Thus far, the bulk of these efforts have focused on understanding bosonic topological phases.
These phases are ``bosonic'' because the topological excitations emerge from bosonic 
local degrees of freedom.

By contrast, much less is known about how to complete a classification program for {\it fermionic} topological phases, in which fermions constitute 
the underlying degrees of freedom. 
Early work in this direction was presented by one of the authors in a series of talks \cite{Walker2013,Walker2014,Walker2015}.
Progress on understanding the coherence relations used to classify fermionic topological phases and the identification of a class of examples of such phases was made in \cite{gu2015,gu2014,Lan2016b}. 
Recently, Majorana dimer lattice models have appeared \cite{Freedman2011a,tarantino2016,ware2016}, 
which give an explicit Hamiltonian construction of a 
non-trivial fermionic phase closely related to the Ising theory. 
There has also been some recent work in the math community \cite{usher2016,brundan2016,bruillard2017,bonderson2017} 
devoted to studying the formal category-theoretic description of fermionic topological phases and spin-TQFTs. 

Intimately related to the description of fermionic topological phases is the concept of fermion condensation, 
whereby one passes to a phase in which the emergent (anyonic) fermions have become 
local particles (meaning that they can be created and destroyed locally). 
There have been several recent approaches related to understanding 
fermionic topological phases with field theoretic methods, fermion condensation, and bosonization \cite{Barkeshli2014b,barkeshli2015,gaiotto2016, bhardwaj2016, bhardwaj2016b,kapustin2017,putrov2016}, 
with a more algebraic take on fermion condensation given in \cite{wan2016}. 

\ethan{I think that to avoid confusion, we should probably only refer to 2+1 dimensional things as ``topological phases'', or else be more explicit about making the distinction between ``fusion theory'' and ``theory with braiding'' to distinguish 1+1 dimensional things from 2+1 dimensional things.}
\dave{Sounds good.}
In this work, we perform a systematic study of fermionic topological phases and fermion condensation from a category-theoretic point of view. 
The strategy we will use to construct examples of fermionic topological phases will be to start with 
a bosonic phase described by a tensor category $\mcc$
which contains an emergent fermion $\psi$.
To obtain a fermionic theory, we will ``condense'' $\psi$.
The resulting fermionic fusion theory is described by a super pivotal category, which we denote
as $\mcc / \psi$.
$\mcc/\psi$ is intrinsically fermionic because in order for a phase to support local fermionic excitations, 
its underlying degrees of freedom must be fermionic. 

Due to their nontrivial spin and statistics, condensing fermions is not a straightforward business. 
From a mathematical perspective, in order to perform the condensation it is necessary to equip the configuration 
space of $\psi$ worldline endpoints with a certain complex line bundle. 
Physically, the construction of this bundle amounts to attaching a phase of physical (not emergent) fermions $f$ 
to the parent bosonic theory: 
fermion condensation then heuristically proceeds by coupling the $\psi$ fermions to 
the $f$ fermions, and condensing $\psi f$ bound states. 
In most cases (when $\psi$ is not transparent in $\mcc$), we will also need to perform 
the condensation with a construction we call the ``back wall'', which is a codimension-1 surface 
on which $\psi$ worldlines are allowed to end. \ethan{Because of this construction, the resulting 
condensed theory ``loses'' the braiding of the parent theory, and thus the condensed theory only describes 
fusion data, not braiding data (and as such describes a 1+1-dimensional theory). The condensed theory can 
then be used as input data to a generalized 
string-net model which produces a braided (2+1-dimensional) fermionic topological phase. }
\dave{Looks OK to me.}

An important difference between fermionic topological phases and their bosonic counterparts is that 
the former possesses two distinct classes of simple objects (or anyons). 
One class of simple objects, which we refer to as ``m-type'' objects, are identical in character
to the simple objects found in bosonic theories. 
The other class of objects, which we call ``q-type'' objects, have no bosonic analogues. 
From a formal perspective, they are distinguished by their nontrivial endomorphism algebras -- if 
$a$ is a q-type simple object, then $\End(a) \cong \cliff_1$, the first complex Clifford algebra. 
From a physical point of view, these can be thought of as ``Majorana objects'', which have the ability 
to ``absorb'' fermions. 
In string-net constructions, strings labeled by q-type objects behave like Kitaev wires in the 
topological phase: the fermion parity of a closed loop of such a string is determined by 
the spin structure inherited by the string, and is delocalized in the sense that fermions living on the q-type string are allowed to fluctuate freely along its length.

One rather trivial way to produce a fermionic phase is to simply form a non-interacting stack of a phase of physical fermions 
and a known bosonic topological phase. 
To obtain examples of fermionic phases that do not arise in this way (which are called ``primitive'' in \cite{Lan2016b}),
it is essential to examine theories that contain q-type objects, which are fundamentally fermionic in nature and which are impossible to obtain in theories constructed through this stacking procedure. 

A categorical description of the condensed phase $\mcc / \psi$ cannot be obtained within the framework 
of regular tensor categories, and one needs to instead adopt the framework of so-called {\it super pivotal tensor categories}. 
The fermionic nature of $\mcc / \psi$ means that the fusion spaces of the theory become super vector spaces 
(as opposed to normal vector spaces), 
tensor products of morphisms and coherence relations like the pentagon identity are modified to account for Koszul signs, 
the pivotal structure of the theory is changed to account for the presence of fermions, and so on.

We should stress that all of the constructions we employ in this paper are mathematically well-defined and 
self-contained, independent of their physical interpretations. 
Most of the paper uses techniques from category theory, TQFTs and string nets to construct what one
might call fermionic Turaev-Viro theory.
This paper is mostly about fermionic TQFTs from this perspective, 
rather than ground states of Hamiltonians. 
Indeed, not until near the end of the paper do we define a fermionic Levin-Wen style Hamiltonian whose ground states coincide with 
the Hilbert spaces of this TQFT.
Foreshadowing the introduction of this Hamiltonian, we will, throughout the paper, talk about physical notions like ``excitations", ``ground state degeneracies", 
etc, even though
strictly speaking this point of view does not make sense until after we have introduced the Hamiltonian.
We emphasize that the Hamiltonian point of view is optional; most of the paper can be viewed as taking place
in the self-contained world of (fermionic) string-net TQFTs.

In order to examine the quasiparticle excitation spectrum of fermionic phases, 
we use the tube category construction \cite{ocneanu1994},\footnote{
Again, it is technically imprecise to call the objects of the tube category ``excitations'' until after we have carefully defined a Hamiltonian.}
which is closely related to the Drinfeld center. \ethan{This allows us to use the fermionic fusion 
theories produced from the fermion condensation procedure to produce examples of 
braided 2+1 dimensional fermionic topological phases.}
\dave{Looks good to me. Although we could probably avoid using 'produce' twice, maybe replace the second one with construct/give? }
In the fermionic context, we must modify the tube category construction to take into account different spin structures on the circle.
For bosonic theories we have the isomorphism $\tube(\mcc)\cong\mcc\times\overline{\mcc}$ \cite{muger2003b} if $\mcc$ is modular, where $\overline{\mcc}$ denotes the opposite category of $\mcc$.
We prove a fermionic version of this isomorphism, namely that 
if $\mcc$ is modular then 
\be 
	\tube(\mcc / \psi) \cong \mcc \times (\overline{\mcc / \psi}).
\ee

Because quasiparticle excitations are associated to circular boundary components of the ambient 
manifold on which the theory is defined, there are two distinct classes of quasiparticles (a.k.a.\ representations of the tube category) in 
fermionic theories: those with anti-periodic fermion boundary conditions around the circle, and 
those with periodic boundary conditions. 
The tubes in the tube category come equipped with spin structures, which gives the tube category a $\zt$ grading
and separates the quasiparticle spectrum in to vortex quasiparticles (those which bind spin structure defects) 
and non-vortex quasiparticles (which are similar in character to the quasiparticles present in bosonic theories). 

The analysis of things related to the tube category, 
like modular transformations, braiding statistics, and the computation of ground state degeneracies on various spin surfaces,
is also modified in the fermionic setting.  
The behavior of the $S$ and $T$ modular transformations on the torus depends on the spin structure of the torus in question, and 
certain relations like $(ST)^3 = \id$ are modified in the fermionic setting, becoming 
$(ST)^3=(-1)^F\id$ where $(-1)^F$ is the fermion parity operator.

We will also show how to construct a commuting projector lattice Hamiltonian 
for fermionic phases, whose excitation spectrum is given by the objects in the fermionic tube category.  
It is similar in character to the Levin-Wen Hamiltonian \cite{levin2005}, 
except that it includes an extra edge term which is responsible for moving fermions along
edges labeled by q-type objects. 
Spin structure defect excitations 
are realized as violations of this edge term, and are linearly confined. 

Finally, we show how to construct a tensor network which produces the ground state 
wavefunction of our lattice Hamiltonian. We do this using a cut-and-glue approach to 
the construction of the Turaev-Viro-Barrett-Westbury state sum, which allows us to write the bosonic partition function
as a tensor contraction. 
We then show how to modify this construction in order to obtain a fermionic version of the TVBW state sum
and a corresponding fermionic tensor network.  

A series of in-depth examples occupies a large portion of this paper.
Our presentation is characterized by an emphasis on examples, 
and we often save formal definitions and more general statements 
for later sections after relevant examples have been presented.  
Many general observations are mixed in with the example sections,
and we stress that the more general sections are intended as a supplement
to the example sections; they are not stand-alone.

In several places in the paper we make use of a fermionic version of a Turaev-Viro type 2+1-dimensional TQFT.
Constructing this TQFT using the techniques of \cite{Walker2006} is straightforward -- one simply replaces oriented manifolds with
spin manifolds and allows for the possibility of non-trivial endomorphism algebras of minimal idempotents.
In the interest of not further increasing the length of this paper, we have not repeated details found in
\cite{Walker2006} here.

\medskip

We now give a quick section-by-section summary of the paper.
Much of the content of Section \ref{C2_condense_sect} was presented at \cite{Walker2013} in July 2013,
and many of the ideas contained in Sections \ref{C2excitations}, \ref{C2_fusion_rules}, and \ref{Super_pivotal_Hamiltonian} were presented at \cite{Walker2014} and again
at \cite{Walker2015}.

Sections \ref{C2_condense_sect} and \ref{C2_quasiparticles} are devoted to a detailed study of 
fermion condensation in the Ising TQFT, which is a simple case study that allows us to build intuition for the condensation procedure.
This condensed theory has been examined before in \cite{bhardwaj2016, kapustin2017}; 
here we examine it in greater detail. 
In Section \ref{C2_condense_sect} we review the Ising TQFT, describe how to perform the 
fermion condensation, and write down the local string-net rules in the condensed theory, 
which we call the $C_2$ theory. 
In Section \ref{C2_quasiparticles} we compute the simple objects of the tube category of the $C_2$ theory,
determine their fusion rules,
compute the ground state degeneracy on the torus, 
and study the modular transformations 
of the theory. 

In Section \ref{generalities}, we present a collection of more general results
on the machinery of fermionic theories. 
We show how to perform fermion condensation in more general settings
and discuss the fermionic version 
of the tube category construction in more generality.
We also discuss how to compute quantum dimensions and fusion rules,
and we prove some general
relations between the total quantum dimensions of condensed theories, their 
parent theories, and their tube categories.
Additionally, we present a Verlinde-type
dimension formula for fermionic theories.

We devote Section \ref{more_on_tubes} to a detailed study of the tube category 
for fermionic theories which result from fermion condensation in a modular tensor category (MTC). 
We introduce several tools for performing calculations in tube categories, 
and use them to prove that if $\mcc$ is an MTC containing a fermion $\psi$, then
$\tube(\mcc/\psi)\cong \mcc\times (\overline{\mcc/\psi})$ as tensor 
categories. We also describe a way of easily computing the modular data for 
$\tube(\mcc/\psi)$. 

Section \ref{so36} is devoted to the example of performing condensation in the $SO(3)_6$ 
and $SU(2)_6$ theories, while Section \ref{halfesix} discusses fermion condensation in the $
\halfesix$ theory. 
Both of these examples are more involved than the $C_2$ theory, 
and illustrate some of the more interesting features of general fermionic topological phases. 

In Section \ref{def_sect} we discuss super pivotal categories from a more formal point of view. 
We show how fermionic fusion spaces are constructed and tensored together, how 
coherence relations like the pentagon identity are modified in the fermionic case, 
and 
explain various other modifications that are necessary in the fermionic case.

Section \ref{Super_pivotal_Hamiltonian} is devoted to a discussion of a lattice Hamiltonian for fermionic theories, which is an extension of the Levin-Wen Hamiltonian. 
It differs most significantly from the Levin-Wen Hamiltonian due to the presence of an edge term, which 
is responsible for allowing fermions to fluctuate across q-type strings.

We show how to construct a tensor network realizing the ground state of our lattice Hamiltonian 
in Section \ref{state_sums}. We first review how to write the partition function of a bosonic theory 
as a tensor contraction in a way amenable to generalization, and then show how our construction 
can be extended to cover the fermionic case. 

In Section \ref{kitaev_wire}, we discuss the Kitaev chain within the framework of super pivotal 
categories. 
We show how the Kitaev chain Hamiltonian and ground-state wavefunctions can be 
succinctly written down using the diagrammatic calculus developed earlier in the paper, and 
discuss connections between the Kitaev chain and the $C_2$ theory. 
This section also provides a connection between our work 
and recent work on fermionic topological phases in the physics community \cite{ware2016,tarantino2016,turzillo2016}. 
The only prerequisite for this section is a brief reading of Section \ref{C2_condense_sect}, and physically-inclined readers less interested in more general mathematical frameworks
are invited to read this section after reading Section \ref{C2_condense_sect}. 

We end with a conclusion and discussion in Section \ref{discussion}. 
Several appendices contain miscellaneous results and mathematical background information. 


%%%%%%%%%%%%%%%%%%
\subsection{Table of notation}
%%%%%%%%%%%%%%%%%%

In partial compensation for the unwieldy length of this paper, we give a table summarizing some of the 
most frequently used and/or least standard notation found herein.

\medskip

\tabulinesep = 2mm
\begin{longtabu}{|X[1,$c]|X[4,l]|}
	\hline
    \mcc 	& tensor category \\ \hline
    \mcc/\psi 	& fermionic quotient of $\mcc$ \\ \hline
    \spc 	& super pivotal tensor category, e.g.~$\mcc/\psi$ \\ \hline
    \scat 	& super linear category \\ \hline
    \sob(\mcc) 	& complete set of representatives of simple objects for $\mcc$ \\ \hline
	\mor(x \to y)	& morphisms from $x$ to $y$ \\ \hline
    \End(x)	& endomorphism algebra of the object $x$; same as $\mor(x\to x)$ \\ \hline
    \cliff_1	& first complex Clifford algebra \\ \hline
    \cc^{r|s} & Super vector space with even dimension $r$ and odd dimension $s$ \\ \hline
    \text{m-type}	& simple object with $\End(x)\cong \cc$ \\ \hline
    \text{q-type}	& simple object with $\End(x)\cong \cliff_1$ \\ \hline
    n_x		& $\dim\End(x)$, 1 if $x$ is m-type and 2 if $x$ is q-type \\ \hline
	\cl(x) & closure of $x$ in either an annulus or torus depending on context \\ \hline
	\cl_W(x) & closure of $x$ with spin structure $W$ assigned to new cycle \\ \hline
	f\cdot g	& the composition of two morphisms $x \xrightarrow{f} y \xrightarrow{g} z$ (arrow order) \\ \hline
	g \circ f	& the composition of two morphisms $x \xrightarrow{f} y \xrightarrow{g} z$ (function order) \\ \hline
	A(Y)	& string nets modulo local relations on a 2-manifold $Y$; predual Hilbert space \\ \hline
	A(Y; c)	& string nets, with fixed boundary condition $c$ on $\bd Y$, modulo local relations \\ \hline
	Z(Y)	& functions on string nets invariant under local relations on a 2-manifold $Y$; dual space $A(Y)^*$; Hilbert space \\ \hline
	Z(Y; c)	& functions on string nets, with fixed boundary condition $c$ on $\bd Y$, invariant under local relations \\ \hline
	Z(M)	& path integral of a 3-manifold $M$ \\ \hline
	Z(M)(c)	& path integral of a 3-manifold $M$, evaluated on a boundary condition $c\in A(\bd M)$ \\ \hline
    \tube(\mcc)	& tube category of $\mcc$ \\ \hline
    \tube^B(\mcc)	& bounding tube category \\ \hline
    \tube^N(\mcc)	& non-bounding tube category \\ \hline
	\tube_{x \to y}	& morphisms from $x$ to $y$ in the tube category \\ \hline
	B, N	& bounding, nonbounding spin structures on the circle \\ \hline
	S^1_B	& spin circle with bounding (anti-periodic) spin structure \\ \hline
	S^1_N	& spin circle with nonbounding (periodic) spin structure \\ \hline
	\unit	& tensor unit in a tensor category; trivial object \\ \hline
	d_a		& quantum dimension of the object $a$; loop value of $a$ \\ \hline
	\theta_a		& twist eigenvalue of the simple object $a$ \\ \hline
	\mcd^2	& $\sum_{a\in \sob(\mcc)} d_a^2$ in bosonic case; $\sum_{a\in \sob(\spc)} d_a^2/n_a$ in fermionic case \\ \hline
\end{longtabu}

